CFRD Screening Survey

### 2022-03-28 Christine Chan/CFRD Screening Survey/cfrd_screening_analysis.Rmd
Update cfrd_screening_analysis.Rmd

>>>>

## Other Diabetes Screening Methods

```{r}
# Combine and format
endo_alt = endo %>% select(Have.you.used.any.of.the.following.tests.to.screen.diagnose.CFRD.in.the.outpatient.setting...please.select.all.that.apply...choice.HbA1c.:Have.you.used.any.of.the.following.tests.to.screen.diagnose.CFRD.in.the.outpatient.setting...please.select.all.that.apply...choice.Other..specify.in.comment..) %>% 
  pivot_longer(everything()) %>% group_by(name) %>% summarise(n = sum(value == "Checked")) 
endo_alt$name = factor(endo_alt$name)
levels(endo_alt$name) = c("CGM","Fasting glucose","2 hr. glucose","HbA1c","Home fingerstick",
                          "Other","Random glucose")
endo_alt$type = "Endocrinologist"

non_endo_alt = non_endo %>% 
  select(Has.your.center.used.any.of.the.following.tests.to.screen.diagnose.CFRD.in.the.outpatient.setting...please.select.all.that.apply...choice.HbA1c.:
           Has.your.center.used.any.of.the.following.tests.to.screen.diagnose.CFRD.in.the.outpatient.setting...please.select.all.that.apply...choice.None.of.the.above.) %>%
  pivot_longer(everything()) %>% group_by(name) %>% summarise(n = sum(value == "Checked")) 
non_endo_alt$name = factor(non_endo_alt$name)
levels(non_endo_alt$name) = c("CGM","Fasting glucose","2 hr. glucose","HbA1c","Home fingerstick",
                              "Other","Other","Random glucose")
non_endo_alt = non_endo_alt %>% group_by(name) %>% summarise(n = sum(n))
non_endo_alt$type = "Directors"

plot_df = data.frame(rbind(endo_alt,non_endo_alt))
t = plot_df %>% pivot_wider(id_cols = name,values_from = n,names_from = type) %>%
  column_to_rownames(.,var = "name")
# Plot
ggplot(plot_df,aes(x = name,y = n,group = type,fill = type)) + 
  geom_bar(stat="identity",position=position_dodge()) +
  theme_bw() + theme(legend.title = element_blank()) + 
  xlab("Other Diabetes Screening Methods")
```

Center directors and endocrinologists were not significantly different in terms of how often they use alternative screening measures (p = 0.116).
